Arrival Management with Open Data

### 2023-04-05 paper.qmd
Update paper.qmd

data preparation

>>>>

This study builds on open trajectory data from Opensky Network. 
Opensky Network is a non-profit organisation and community-based surveillance data collection network. 
The collected air traffic data is available to researchers and government organisations on a license-free basis.
Performance monitoring is based on the principle of reproducibility and transparency. 
Open access to the underlying data and enrusing reproducibility of the analysis is a key requirement [@PRC_OPDI2022).
